Mapping Microblog Posts to Encyclopedia Articles

### 2011-02-23 lids/twittersearchwrap/paper/paper.tex
added open issues in conclusion

coherent semantic description. \newline\linebreak Coming back to the example,
the output RDF document containes the following triples to reference the

@@

>>>>

coherent semantic description in the RDF document. \newline\linebreak Coming
back to the example, the output RDF document contains the following triples to reference the

@@

@@@ not possible to map one hashtag to a single dbpedia concept: \#ka may be used for Karlsruhe or Ford Ka

@@@ tricky to deal with different languages - wikifier (or any nlp technique) is language dependent, but the trending topics may be commented on in a variety of languages

@@@ how to select external data (parse text from HTML, which part of web page to select - boilerplate stuff might spoil the results (reference blog cleansing paper
